\section{Bootstrapping Taxonomy}

There has been a large amount of previous research on the various bootstrapping techniques for securely pairing devices. Out-of-band (OOB) channels are auxiliary to the main frequency of communication and are used as a means to bolster security. OOB channels are characterized by the uncommon or unused frequencies that the protocols used to communicate or share any cryptographic information they normally would not send on the 2.4 Ghz frequency range.

\subsection{Bluetooth Low Energy (BLE)}
\subsubsection{Device Provision Protocol (DPP)}
As a means for device onboarding, BLE is a viable alternative to Wifi in scenarios that do not require long range communication - not unlike an office. BLE lets a user send out a broadcast that states their intent to bootstrap with another device. The DPP requires two devices: a configurator that broadcasts intent and an enrollee within range that responds to a broadcast. When an enrollee does respond to a broadcast, the devices move to an auxiliary channel via BLE and exchange cryptographic information. One of the primary DPP characteristics is that the configurator sends out a request packet on the auxiliary channel and the enrollee must send back that same auxiliary channel request information to successfully onboard. One of the main vulnerabilities of using BLE pairing is its that broadcasts openly to any device within range. By broadcasting openly, the devices make themselves susceptible to Man in The Middle (MiTM) attacks. BLE itself does not have a proof of possession of the bootstrapping keys in the auxiliary channel. Any device within range can possibly eavesdrop on both device and obtain the bootstrapping keys.


\subsection{Buttons}
\subsubsection{Button Enabled Device Association (BEDA)}
The BEDA protocol is reliant on physical buttons on two devices. These buttons are integral to the protocol because it uses the duration of a pressed button which is used to generate a shared secret This method presents a few vulnerabilities, however. The protocol is vulnerable to replay attacks because hashes are not encrypted when they are sent out which lets an attacker pose as the sender by sending the hash to the original receiving device.

\subsection{Magnetometer Pairing}
Magnetometer pairing is technique of bootstrapping that was designed for smartphones by making use of their magnetometers and a WiFi connection. To initiate the process two devices must be tapped together which should trigger the protocol depending on the threshold that has been set. Once the process has been initiated the devices will go through a standard Diffie-Hellman (DH) Key Exchange. During this process the devices will record their magnetometer readings at the same time. In order to foil eavesdroppers, the protocol makes use of the Interlock protocol to bolster its security against passive attacks. The protocol is secure against MiTM attacks because the Interlock the attacker will only receive half of an encrypted message of which is has no key to decrypt. Magnetometer pairing makes use of the randomness of the strength of magnetic fields by incorporating the lack of temporal or spatial alignment between devices into
